Accelerating structure-function mapping using the ViVa webtool to mine natural variation

### 2019-01-10 manuscript/05-acknowledgments.Rmd
submitted

The authors would like to thank Oghenemega Okolo for assistance testing the ViVa software, and Song Li and Bo Zhang for helpful comments on the manuscript. This work was supported by the National Institute of Health (R01-GM107084) and the Howard Hughes Medical Institute. R.C.W. received fellowship support from the National Science Foundation
(DBI-1402222). B.L.M. and H.K. received support from the M.J. Murdock Charitable Trust. A.R.L. is a Simons Foundation Fellow of the Life Sciences Research Foundation.

>>>>

The authors would like to thank Oghenemega Okolo for assistance testing the ViVa software, and Song Li and Bo Zhang for helpful comments on the manuscript. This work was supported by the National Institute of Health (R01-GM107084), the National Science Foundation (IOS-1546873) and the Howard Hughes Medical Institute. R.C.W. received fellowship support from the National Science Foundation (DBI-1402222). B.L.M. and H.K. received support from the M.J. Murdock Charitable Trust. A.R.L. is a Simons Foundation Fellow of the Life Sciences Research Foundation. A.L. was supported by an NSF Graduate Research Fellowship DGE-1256082.

### 2019-01-10 manuscript/index.Rmd
submitted

---
title: Accelerating structure-function mapping using the ViVa webtool to mine natural variation 
shorttitle: 'ViVa: Visualizing Variation' 
author:
  - Morgan O. Hamm^1^, Britney L. Moss^2^, Alexander R. Leydon^1^,  Hardik P. Gala^1^,  Amy Lanctot^1^, Romi Ramos^1^, Hannah Klaeser^2^, Andrew C. Lemmex^1^, Mollye L. Zahler^1^, Jennifer L. Nemhauser^1^, R. Clay Wright^3^$*$ 
  - ^1^Department of Biology, University of Washington, Seattle, WA, USA.
  - ^2^Department of Biology, Whitman College, Walla Walla, WA, USA. 
  - ^3^Biological Systems Engineering, Virginia Tech, Blacksburg, VA, USA. Previous affiliation$:$ Department of Biology, University of Washington, Seattle, WA, USA.
  - $*$Direct correspondence to$:$ wrightrc@vt.edu.

@@

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE, collapse = TRUE, comment = "#>", tidy = TRUE, cache = TRUE, cache.lazy = FALSE, fig.height=4, fig.width=7, dpi = 600, out.extra='style="margin: auto; display: block; padding-top: 15px;"')

>>>>

---
title: Accelerating structure-function mapping using the ViVa webtool to mine natural variation 
shorttitle: 'ViVa: Visualizing Variation' 
author:
  - Morgan O. Hamm^1^, Britney L. Moss^2^, Alexander R. Leydon^1^,  Hardik P. Gala^1^,  Amy Lanctot^1^, Román Ramos^1^, Hannah Klaeser^2^, Andrew C. Lemmex^1^, Mollye L. Zahler^1^, Jennifer L. Nemhauser^1^, R. Clay Wright^3^$*$ 
  - ^1^Department of Biology, University of Washington, Seattle, WA, USA.
  - ^2^Department of Biology, Whitman College, Walla Walla, WA, USA. 
  - ^3^Biological Systems Engineering, Virginia Tech, Blacksburg, VA, USA. Previous affiliation$:$ Department of Biology, University of Washington, Seattle, WA, USA.
  - $*$Direct correspondence to$:$ wrightrc@vt.edu.

@@

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, 
  message = FALSE, 
  echo = FALSE,
  collapse = TRUE, 
  comment = "#>", 
  tidy = TRUE, 
  cache = TRUE, 
  cache.lazy = FALSE, 
  fig.height=4, 
  fig.width=7, 
  dpi = 600, 
  out.extra='style="margin: auto; display: block; padding-top: 15px;"')
